Efficiently summarizing relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-23 treestats_paper.tex
funding

\include{macros}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Acknowledgments}
Thanks to Graham Coop, Andrew Kern, Nick Patterson, Kelley Harris and
Aaron Ragsdale for useful suggestions
and to Leo Speidel for providing the inferred 1000 Genomes tree sequence.

>>>>

\include{macros}
\newif\ifreviewresponses
\reviewresponsestrue  % include them
% \reviewresponsesfalse  % don't include them
\newcommand{\responsefile}{review-responses.tex}  % name of the review reponses file
\input{review-response-commands} % for line numbers only for now

@@

%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and code accessibility}

All methods described here are implemented in python and C in the package \tskit{},
available from \url{https://github.com/tskit-dev/tskit}
under the terms of the MIT license.
All code used to produce the figures in this paper
is available from \url{https://github.com/petrelharp/treestats_ms}.

@@

%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Acknowledgments}
Thanks to Graham Coop, Andrew Kern, Nick Patterson, Kelley Harris and
Aaron Ragsdale for useful suggestions
and to Leo Speidel for providing the inferred 1000 Genomes tree sequence.
This work was supported by NSF grant \#1262645 (DBI) to PLR
and by NIH grant R01-GM115564 to KRT. JK was supported by
the Robertson Foundation and Wellcome Trust grant 100956/Z/13/Z
to Gil McVean.
